Modelling BCG vaccination in the UK

### 2019-05-03 rmds/index.Rmd
pushing fixes

---
output: html_document
---

```{r}
## Wordcount: 2811
```

@@

* **Chapter \@ref(discussion):** Results from all previous Chapters are summarised and discussed as a whole. The strengths and weaknesses of the analysis in this thesis are outlined. Further work is suggested. Future work is outlined.

>>>>

---
author: 'Samuel Abbott'
date: 'May 2019'
division: 'Bristol Medical School: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "41,218"
knit: bookdown::render_book
site: bookdown::bookdown_site
always_allow_html: yes
output: 
  thesisdown::thesis_pdf: default
  thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
abstract: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = ' ')`
acknowledgements: >
 `r if(knitr:::is_latex_output()) paste(readLines("00-acknowledgements.Rmd"), collapse = ' ')`
declaration: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-declaration.Rmd"), collapse = ' ')`
contribution: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-contribution.Rmd"), collapse = ' ')`
bibliography: bib/thesis.bib
#Download your specific bibliography database file and refer to it in the line above.
csl: csl/bmj.csl
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
---

```{r knitr-options, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi = 320, 
                      fig.width = 8, fig.height = 8,
                      out.width = "80%", fig.align = 'center')
```

```{r include_packages, include = FALSE}
if (!require(devtools))
  install.packages("devtools", repos = "http://cran.rstudio.com")
if (!require(thesisdown))
  devtools::install_github("ismayc/thesisdown")
library(thesisdown)
if (!require(tidyverse))
  install.packages("tidyverse", repos = "http://cran.rstudio.com")
PaperTheme <- ggplot2::theme_minimal() +
  theme(legend.position = "top")
ggplot2::theme_set(PaperTheme)
```

@@

* **Chapter \@ref(discussion-chapt):** Results from all previous Chapters are summarised and discussed as a whole. The strengths and weaknesses of the analysis in this thesis are outlined. Further work is suggested. Future work is outlined.
